### 2019-03-24 tex/chapter/definicoes.tex
WIP

Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points. For example, the elliptical distance between the points $p,q \in \R^2$ is $||p-q||_{elliptical}$.

@@

The ellipse is categorized, along with the parabola and the hyperbola, as a conic section. As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation that describes any conic section is given as follows

@@

Any ellipse, rotated or axis-parallel, can be described by \autoref{equation:quadratic_form}. To distinguish an ellipse from the other conic sections the condition $4AC - B^2>0$ can be verified \cite{ayoub}.

Then, assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows

@@

An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{the only non-zero terms are in the main diagonal}. This can be understood as a scaling transformation applied to the euclidean norm.
Defining the matrix $Q$ as

>>>>

Determining the distance between two points, given a norm function is done by calculating the norm of the vector defined by the difference between the two points. For example, the elliptical distance between the points $p,q \in \R^2$ is given by $||p-q||_{elliptical}$.

@@

The ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. As the name suggests, conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation that describes any conic section is given as follows

@@

Any ellipse, rotated or axis-parallel, can be described by \autoref{equation:quadratic_form}. To distinguish an ellipse from the other conic sections given an instance of \autoref{equation:quadratic_form}, the condition $4AC - B^2>0$ can be verified \cite{ayoub}.

Assuming the center of an ellipse is $c \in \R^2$, then \autoref{equation:quadratic_form} can be rewritten as a quadratic form as follows

@@

An axis parallel ellipse centered at $c = (c_x,c_y)$ can be described using \autoref{def:ellipse} with $Q$ being a diagonal matrix \footnote{The only non-zero terms are in the main diagonal}. This can be understood as a scaling transformation applied to the euclidean norm.
Defining the matrix $Q$ as

### 2019-03-24 tex/chapter/future.tex
WIP

In this work, we defined the problem of planar maximal covering by disks, we called it $MCD$, and proposed a method for it based on previous works that we found. This method established the basis of our work, as after defining the ellipses counterpart problem, we developed a method based on that algorithm which needed very little modification. To compare results with \cite{andreta}, a small change needs to be done in the algorithm because their version of the problem contains another constraint: out of the $m$ ellipses given, the solution can use exactly $k$ of them. This change as well as the comparison of results is left as future work.

The $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} is also a subject of future work and is set as the primary goal for this master's research. We want to develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

Also, in \cite{aronov:2008} a Monte Carlo approximation is presented for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. An adaptation for the multiple ellipses case is left as a secondary goal for the final version of this work.

Finally, the version of the problem where every ellipse can be freely rotated is left as a subject of study for the future. In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time. Because of that, a stochastic global optimization method was proposed, it performed well and was able to obtain an optimal solution for small cases. The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.

>>>>

To take advantage of the great amount of works which were found in the literature,
 we decided to first introduce the planar maximal covering by disks problem, develop a method for it, and just then adapt it for the ellipses case. It turned out that because of the similarities between the two problems, adapting was possible and actually very simple. This made the method developed by us have a very different approach than the ones in \cite{andreta} and \cite{canbolat}. The next step is to implement it and compare the results that \cite{andreta} obtained.

As of future work, we intend to study $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

Also, the version of the problem where every ellipse can be freely rotated is set as a primary goal for this master's research. In \cite{andreta}, the deterministic method developed by them could not obtain solutions for moderate-to-large instances within reasonable time. Because of that, a stochastic global optimization method was proposed, it performed well and was able to obtain an optimal solution for small cases. The goal we have in mind for the future is to develop an exact method that takes into consideration the algorithm we developed for the axis-parallel version of the problem and compare the results.

Finally, as a secondary goal, we want to develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse, the case with more than one is left as a challenge for us for the next steps of our research.

### 2019-03-24 tex/chapter/introducao.tex
WIP

This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work. Also, the \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.

>>>>

This work is structured in the following way: \autoref{chapter:definitions} introduces some definitions and results that are used throughout the next chapters; in \autoref{chapter:pmclp}, the maximal covering by disks problem is studied and a $\bigO(n^{2m})$ algorithm is proposed; in \autoref{chapter:ellipses}, the maximal covering by ellipses is introduced and the algorithm for the disks case is adapted for it; finally, \autoref{chapter:future_work} presents what is left as future work. Also, \autoref{chapter:ellipses_intersection} determines with detail the intersection of two ellipses, which is used in the algorithm developed in \autoref{chapter:ellipses}.
